Constructive Preference Elicitation by Setwise Max-margin Learning

### 2016-01-26 paper/ijcai16.tex
paper: added lasso refs

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them~\cite{} \stefano{@Paolo: add refs}. The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{lasso}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}).

@@

In all experiments we use an internal 5-fold cross-validation procedure to
update the hyperparameters $\alpha$, $\beta$, and $\gamma$ after every 5
iterations. The hyperparameters are chosen as to minimize the ranking loss over
the user responses collected so far. $\alpha$ is taken in $\{20, 10, 5, 1\}$,
while $\beta$ and $\gamma$ are taken in $\{10, 1, 0.1, 0.001\}$\footnote{Note
that $\alpha$ can not be taken to be less than $1$, as in this case, the
objective can be increased arbitrarily while keeping the right-hand side of
Eq.~(\ref{eq:wyconstr}) constant, rendering the problem unbounded.}.

>>>>

The third part of the objective does require a more in depth explanation. In
many scenarios the user will have strong preferences about some attributes, but
will be indifferent to most of them~\cite{} \stefano{@Paolo: add refs}. The $\ell_1$ penalty is frequently
used to improve the sparsity of learned models~\cite{lasso,zhang2008,Hensinger2010}, with consequent gains
in generalization ability and efficiency, as confirmed by our empirical
findings (see Section~\ref{sec:experiments}).

@@

In all experiments we use an internal 5-fold cross-validation procedure to
update the hyperparameters $\alpha$, $\beta$, and $\gamma$ after every 5
iterations. The hyperparameters are chosen as to minimize the ranking loss over
the user responses collected so far. $\alpha$ is taken in $\{20, 10, 5, 1\}$,
while $\beta$ and $\gamma$ are taken in $\{10, 1, 0.1, 0.001\}$.\footnote{Note
that $\alpha$ can not be taken to be less than $1$, as in this case, the
objective can be increased arbitrarily while keeping the right-hand side of
Eq.~(\ref{eq:wyconstr}) constant, rendering the problem unbounded.}
